Is it possible to predict the reproductive success of selfing and pollinated plants based on its flower-insect interactions? 

This question could be addressed using a logistic regression or SVM where the predictor variables are the flower-insect interactions and the target variable is the seed mass or number of fruits produced. This question could be addressed using a support vector machine to develop a classification or regression model that separates high- and low-fruit producing plants based on their flower-insect interaction patterns. 

~~~

Libraries
```{r}

library(ggplot2)
library(dplyr)
library(e1071)

```
Load data
```{r}

data <- read.csv("C:/Users/Kerri/OneDrive - Queen's University/5th year/Winter/BIOL432/BIOL432_FinalProject/Soper_Gorden_Adler_AJB_2018_Flower_Insect_Interactions_Processed_Data.csv")

```



This question could be addressed using a logistic regression or SVM where the predictor variables are the flower-insect interactions and the target variable is the seed mass or number of fruits produced. This question could be addressed using a support vector machine to develop a classification or regression model that separates high- and low-fruit producing plants based on their flower-insect interaction patterns. 


Logistic regression - number of flower-insect interactions vs seed mass
```{r}
total <- data %>% select("Plot_Number", "Treatment",
                        "Average_CH_Seed_Mass","Average_CL_Seed_Mass",
                        "Pollinators_Per_Hour", "Robbers_Per_Hour", "Thieves_Per_Hour") %>%
  mutate(Total_Average_Seed_Mass = Average_CH_Seed_Mass + Average_CL_Seed_Mass)

ggplot(data = na.omit(total), aes(x = Pollinators_Per_Hour, y = Total_Average_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
Totpol <- lm(Total_Average_Seed_Mass~Pollinators_Per_Hour, data = seed)
summary(Totpol)

ggplot(data = na.omit(total), aes(x = Robbers_Per_Hour, y = Total_Average_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
Totrob <- lm(Total_Average_Seed_Mass~Pollinators_Per_Hour, data = seed)
summary(Totrob)

ggplot(data = na.omit(total), aes(x = Thieves_Per_Hour, y = Total_Average_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
Totthi <- lm(Total_Average_Seed_Mass~Pollinators_Per_Hour, data = seed)
summary(Totthi)




CH <- data %>% select("Plot_Number", "Treatment",
                        "Average_CH_Seed_Mass",
                        "Pollinators_Per_Hour", "Robbers_Per_Hour", "Thieves_Per_Hour")

ggplot(data = na.omit(CH), aes(x = Pollinators_Per_Hour, y = Average_CH_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
CHpol <- lm(Average_CH_Seed_Mass~Pollinators_Per_Hour, data = CH)
summary(CHpol)

ggplot(data = na.omit(CH), aes(x = Robbers_Per_Hour, y = Average_CH_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
CHrob <- lm(Average_CH_Seed_Mass~Robbers_Per_Hour, data = CH)
summary(CHrob)

ggplot(data = na.omit(CH), aes(x = Thieves_Per_Hour, y = Average_CH_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
CHthi <- lm(Average_CH_Seed_Mass~Thieves_Per_Hour, data = CH)
summary(CHthi)




CL <- data %>% select("Plot_Number", "Treatment",
                        "Average_CL_Seed_Mass",
                        "Pollinators_Per_Hour", "Robbers_Per_Hour", "Thieves_Per_Hour")

ggplot(data = na.omit(CL), aes(x = Pollinators_Per_Hour, y = Average_CL_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
CLpol <- lm(Average_CL_Seed_Mass~Thieves_Per_Hour, data = CL)
summary(CLpol)

ggplot(data = na.omit(CL), aes(x = Robbers_Per_Hour, y = Average_CL_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
CLrob <- lm(Average_CL_Seed_Mass~Thieves_Per_Hour, data = CL)
summary(CLrob)

ggplot(data = na.omit(CL), aes(x = Thieves_Per_Hour, y = Average_CL_Seed_Mass)) +
  geom_point() +
  geom_smooth(method = "lm")
CLthi <- lm(Average_CL_Seed_Mass~Thieves_Per_Hour, data = CL)
summary(CLthi)

```

NDMS

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ape)
library(ggtree)
library(vegan)
```

Data
```{r}
data <- read.csv("C:/Users/Kerri/OneDrive - Queen's University/5th year/Winter/BIOL432/BIOL432_FinalProject/Soper_Gorden_Adler_AJB_2018_Flower_Insect_Interactions_Processed_Data.csv") %>% select(c(Robbing,Florivory,Pollination,Average_Seeds_Per_CH_Fruit,Average_Seeds_Per_CL_Fruit,Average_CH_Seed_Mass,Average_CL_Seed_Mass))

longdata <- gather(data, interaction, yn, Robbing:Pollination, factor_key = T) %>% na.omit() %>% filter(!yn == "N")

```


For CH
```{r}
nmdsCHdata <- longdata %>% select(c(Average_Seeds_Per_CH_Fruit,Average_Seeds_Per_CL_Fruit,Average_CH_Seed_Mass,Average_CL_Seed_Mass)) 
factors <- longdata %>% select(interaction) %>% mutate(Plot = row.names(longdata))

nmdsCHdist <- vegdist(nmdsCHdata, method = "bray", binary = F)
nmdsCHtree <- nj(nmdsCHdist)

NMDSCHdat <- metaMDS(nmdsCHdist, k = 2, trymax = 100)

PDatCH <- data.frame(NMDS1 = NMDSCHdat$points[,1],
                   NMDS2 = NMDSCHdat$points[,2],
                   Plot = row.names(nmdsCHdata))

PDatCH <- merge(PDatCH, factors, by = "Plot", all.x = T, all.y = F)

ggplot(data = PDatCH) +
  geom_point(aes(x = NMDS1, y = NMDS2, colour = interaction)) +
  scale_colour_discrete(name = "Interaction") +
  theme_classic()

CH_Mating <- betadisper(nmdsCHdist, group = factors$interaction)
permutest(CH_Mating)
plot(CH_Mating, hull=FALSE, ellipse=TRUE) ##sd ellipse

```


Is it possible to predict the reproductive success of selfing and pollinated plants based on its flower-insect interactions? 

in NDMS figure - shape by insects and colour by mating type


For CL
```{r}
nmdsCLdata <- longdata %>% select(c(Average_Seeds_Per_CL_Fruit,Average_CL_Seed_Mass)) 

nmdsCLdist <- vegdist(nmdsCLdata, method = "bray", binary = F)
nmdsCLtree <- nj(nmdsCLdist)

NMDSCLdat <- metaMDS(nmdsCLdist, k = 2, trymax = 100)

PDatCL <- data.frame(NMDS1 = NMDSCLdat$points[,1],
                   NMDS2 = NMDSCLdat$points[,2],
                   Plot = row.names(nmdsCLdata))

PDatCL <- merge(PDatCL, factors, by = "Plot", all.x = T, all.y = F)

ggplot(data = PDatCL) +
  geom_point(aes(x = NMDS1, y = NMDS2, colour = interaction)) +
  scale_colour_discrete(name = "Interaction") +
  theme_classic()

CL_Mating <- betadisper(nmdsCLdist, group = factors$interaction)
permutest(CL_Mating)
plot(CL_Mating, hull=FALSE, ellipse=TRUE)

```



