---
title: "Random Forests (Q3)"
author: "Rishona Vemulapalli (20164619)"
date: "2023-03-23"
output: html_document
---

Research Question #3: Can we identify the most important variables that influence plant reproductive success and use them to develop a decision tree that can guide plant breeding efforts? 

Details: This question could be addressed using a decision tree to identify the most important variables that contribute to plant reproductive success and to develop a breeding strategy that focuses on optimizing those variables.

NOTES:
- Have to do decision tree first, to find most important
- Variable must be binary? (0s and 1s) Seed mass? Add them
- Will have to determine what best represents a threshold for reproductive success
- Threshold (average of the column) potentially, have to see what makes sense
    - Below threshold = 0, above threshold = 1
- Decision tree will tell you what threshold it split on for each variable (the first is the most important)
- Response variable for decision tree is same for random forest. 
- Number of seeds?
- Do a histogram (would be best if histogram is not normally distributed)

----------------------------

### Setup:
```{r message = FALSE}
library(ggplot2)
library(dplyr)
library(tree)
library(rpart)
library(gbm)
library(randomForest)
```

### Load the data
```{r}
Dat <- read.csv("./data/Soper_Gorden_Adler_AJB_2018_Flower_Insect_Interactions_Processed_Data.csv")
```

# Lets just use CL bc CH sucks
```{r}
# Checking distribution of data
hist(Dat$Average_CL_Seed_Mass)
```

Remove CH column:
```{r}
Dat2 <- Dat %>%
  select(-c(Plot_Number, Average_CH_Seed_Mass, Date_of_First_CH_Flower))
```

Checking summary stats for the average CH seed mass:
```{r}
summary(Dat2$Average_CL_Seed_Mass)
```

Remove all rows with NA's (to exclude the 59 NAs in the seed mass volume)
```{r}
Dat3 <- Dat2[complete.cases(Dat2$Average_CL_Seed_Mass), ]
```

Summary to see new mean of CL seed mass (after NAs removed)
```{r}
summary(Dat3$Average_CL_Seed_Mass)
```

Make Average CL seed mass into a binary response variable (mean and above = Success, below = Dead)
```{r}
Dat3$Binary_Avg_Seed_Mass <- ifelse(Dat3$Average_CL_Seed_Mass > mean(Dat3$Average_CL_Seed_Mass), "Success", "Dead")
Dat3$Binary_Avg_Seed_Mass <- as.factor(Dat3$Binary_Avg_Seed_Mass)
```

Remove Average CL Seed Mass Column
```{r}
TreeDat <- Dat3 %>%
  select(-c(Average_CL_Seed_Mass))

TDat <- TreeDat %>%
  mutate(Treatment = as.factor(Treatment),
         Robbing = as.factor(Robbing), 
         Florivory = as.factor(Florivory),
         Pollination = as.factor(Pollination))
```

```{r}
# Split the processed_data dataframe into training and test sets using a 70/30 split ratio
split <- sample.split(TDat$Binary_Avg_Seed_Mass, SplitRatio = 0.7)
train <- TDat[split,]
test <- TDat[!split,]
```


<<<<<<< HEAD
Make the tree
```{r}
# Build the decision tree model
SeedMassTree <- rpart(Binary_Avg_Seed_Mass ~ ., data = train, method = "class")
# Plot the decision tree
rpart.plot(SeedMassTree, fallen.leaves = TRUE)
```

```{r}
seed_mass_predictions <- predict(SeedMassTree, newdata = test, type = "class")


```